\documentclass[draftclsnofoot,onecolumn,10pt,compsoc]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage{url}
\usepackage{hyperref}

\usepackage{graphicx} %package to manage images
\graphicspath{ {images/} }

\usepackage{enumitem}

\usepackage[letterpaper, margin=.75in]{geometry}

\newcommand{\toc}{\tableofcontents}

\usepackage{hyperref}
\usepackage{listings}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\renewcommand{\lstlistingname}{Code Example} % a listing caption title.
%\renewcommand{\lstlistlistingname}{List of \lstlistingname s} % list of lists -> list of Thread Program
\lstset{
    frame=single,
    language=C,
    columns=flexible,
    numbers=left,
    numbersep=5pt,
    numberstyle=\tiny\color{gray},
    keywordstyle=\color{blue},
    commentstyle=\color{dkgreen},
    stringstyle=\color{mauve},
    breaklines=true,
    breakatwhitespace=true,
    tabsize=4,
    captionpos=b
}

\def\name{Terrance Lee }

%% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = false,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {},
  pdftitle = {},
  pdfsubject = {},
  pdfpagemode = UseNone
}

\parindent = 0.0 in
\parskip = 0.1 in

\begin{document}

\begin{titlepage}
	\title{Project 2}
	\author{CS444 - Spring 2017 \\ Terrance Lee, Raja Petroff, Markus Woltjer}
	\maketitle
	\begin{abstract}
		The following document contains information about project 2 which includes the design plan of SSTF algorithm, version control, work done and dining philosophers problem explanation.  
	\end{abstract}
	
	\thispagestyle{empty} % gets rid of the "0" page number.
	
\end{titlepage}
%\newpage

\tableofcontents

\newpage

\section{The design we planned to use to implement the SSTF algorithms.}
\section{Version Control Log}
\begin{center}
	\begin{tabular}{| p{0.3\linewidth} | p{0.3\linewidth} | p{0.3\linewidth} |}
		\hline User & Commit Message & Date\\
		\hline terrancelee81 & Added Makefile & May 4th\\
		\hline terrancelee81 & added latex docs& May 4th\\
		\hline petroffr & updated Makefile report & May 5th \\	
		\hline petroffr & added sstf scheduler file & May 5th \\ 	
		\hline markuswoltjer & added Concurrency2.c & May 5th\\
		\hline markuswoltjer & added Philosophers.c & May 5th\\	
		\hline markuswoltjer & updated Philosophers.c & May 7th\\	
		\hline markuswoltjer & added all fork status to Philosophers.c & May 8th\\
		\hline terrancelee81 & updating  latex docs & May 8th\\	
	\end{tabular}
\end{center}
\section{Work Log}
\begin{itemize}
	\item May 2th - began working on the kernel part of the assignment
	\item May 4th - Configured SSTF
	\item May 5th - Makefile got updated
	\item May 5th -  Concurrency added
	\item May 5th - Philosphers added
	\item May 5th - update Makefile to Compile report
	\item May 7th - updated Philosphers 
	\item May 8th - added all fork status to Philosphers
	\item May 8th - updated latex docs
	
	
	
	
\end{itemize}
\section{}
\subsection{What do you think the main point of this assignment is?}
To make us understand the scheduler and how to better use schedulers.  With this assignment we are learning how to scheduler our task and make the operating system more efficient 
\subsection{How did you personally approach the problem? Design decisions, algorithm, etc.}
When approaching this problem we took a look how to change the sstf\_add\_request.  While looking at this function this think about other items like whether we would need to change to include what would need to work.  For testing Raja was looking at how to test with python.
\subsection{How did you ensure your solution was correct? Testing details, for instance.}
We print out the sector numbers and we plot them to make sure they are merged correctly.  
We are just using printk statements, we also used some python to do the ploting. 

\subsection{What did you learn?}
How to sort sectors and how to merge correctly, while how to debug the kernel. We also learned how disc I/O works and how to write our own elevator algorithm. Also we learned a little more about when a teammate is unavailable due to other issues how to come together as a team and still get the assignment done. 




\end{document}
